Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-15 Paper/paper.tex
Have added a sentence justifying why we choose worst case equilibria

The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set.
In case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour.

>>>>

The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set.
In case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour \cite{TimRoughgarden}.
